Reproducible Research in R: A Tutorial on How to Do the Same Thing More \highlighting{Than Once}

### 2021-12-04 manuscript.tex
wrap things up

%=================================================================
\firstpage{1}
\makeatletter
\setcounter{page}{\@firstpage}
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{5}
\pubyear{2019}
\copyrightyear{2019}
\externaleditor{Academic Editor: {Alexander Robitzsch}} %MDPI: Please add the academic editor.
\datereceived{} 
\dateaccepted{} 
\datepublished{}
\hreflink{https://doi.org/} % If needed use \linebreak

@@

Unfortunately, Docker requires administrator rights to run, which may
not be available to all researchers. We recommend {\texttt{renv}}
(\url{https://rstudio.github.io/renv/articles/renv.html})
\citep{R-renv} in cases where no administrator rights can be obtained
but we can not detail its use in this document. \texttt{renv} tracks which
R package is installed from which source in which version in a so-called \hl{\texttt{lockfile}}
(\url{https://rstudio.github.io/renv/articles/lockfile.html}).
This lockfile is then used to reinstall the same packages on other
computers or later in time. For a more thorough discussion, see
Lissa~et~al.~\citep{vanlissa2020worcs}.

Start RStudio and install the package \hl{\texttt{repro}}
(\url{https://github.com/aaronpeikert})~\citep{R-repro}.
It will assist you while you follow the tutorial.

@@

The workflow described in this paper facilitates a rigorous solution to
this problem: Instead of describing the analysis in prose, researchers
include the code required to conduct the analysis in the
preregistration. We term this approach of writing and publishing code at
the preregistration stage \emph{Preregistration as Code (PAC)}. PAC has
the potential to eliminate undisclosed researchers degrees of freedom to
a much greater extent than, e.g., preregistration templates. Moreover,
it reduces overhead by removing the need to write a separate
preregistration and manuscript. For PAC, researchers can write a
reproducible, dynamically generated draft of their intended manuscript
at the preregistration stage. This already includes most of the typical
sections, such as introduction, methods, and results. These results are
initially based on simulated data with the same structure as the data
the authors expect to obtain from their experiments. For guidance on how
to simulate data, see Morris~et~al.~\citep{morrisUsingSimulationStudies2019},
Paxton~et~al.~\citep{paxtonMonteCarloExperiments2001}, and
Skrondal~\citep{skrondalDesignAnalysisMonte2000}, as well as the R packages
{\texttt{simstudy}} 
\mbox{ (\url{https://cran.r-project.org/web/packages/simstudy/vignettes/simstudy.html})}
~\citep{simstudy} and
{\texttt{psych}} (\url{https://personality-project.org/r/psych/help/sim.html})
\citep{psych}.

@@

\begin{quote}
\hl{Navigate to} %MDPI: Please add the accessed date.
 \url{https://zenodo.org/account/settings/github/}
\end{quote}

@@

Supplementary Materials{All materials (i.e., the source code, all figures, and the data) that are neccesary for reproducing the submitted version of this article are availible at \url{https://github.com/aaronpeikert/repro-tutorial} and archived under \url{https://doi.org/10.5281/zenodo.5724454}.

>>>>

%=================================================================
\firstpage{1}
\makeatletter
\setcounter{page}{\@firstpage}
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{5}
\pubyear{2019}
\copyrightyear{2019}
\externaleditor{Academic Editor: {Alexander Robitzsch}}
\datereceived{} 
\dateaccepted{} 
\datepublished{}
\hreflink{https://doi.org/} % If needed use \linebreak

@@

Unfortunately, Docker requires administrator rights to run, which may
not be available to all researchers. We recommend
\href{https://rstudio.github.io/renv/articles/renv.html}{\texttt{renv}}
\citep{R-renv} in cases where no administrator rights can be obtained
but can not detail its use in this document. \texttt{renv} tracks which
R package is installed from which source in which version in a so-called
\href{https://rstudio.github.io/renv/articles/lockfile.html}{\texttt{lockfile}}.
This lockfile is then used to reinstall the same packages on other
computers or later in time. For a more thorough discussion, see
Lissa~et~al.~\citep{vanlissa2020worcs}.

Start RStudio and install the package
\href{https://github.com/aaronpeikert}{\texttt{repro}}\citep{R-repro}.
It will assist you while you follow the tutorial.

@@

The workflow described in this paper facilitates a rigorous solution to
this problem: Instead of describing the analysis in prose, researchers
include the code required to conduct the analysis in the
preregistration. We term this approach of writing and publishing code at
the preregistration stage \emph{Preregistration as Code (PAC)}. PAC has
the potential to eliminate undisclosed researchers degrees of freedom to
a much greater extent than, e.g., preregistration templates. Moreover,
it reduces overhead by removing the need to write a separate
preregistration and manuscript. For PAC, researchers can write a
reproducible, dynamically generated draft of their intended manuscript
at the preregistration stage. This already includes most of the typical
sections, such as introduction, methods, and results. These results are
initially based on simulated data with the same structure as the data
the authors expect to obtain from their experiments. For guidance on how
to simulate data, see Morris~et~al.~\citep{morrisUsingSimulationStudies2019},
Paxton~et~al.~\citep{paxtonMonteCarloExperiments2001}, and
Skrondal~\citep{skrondalDesignAnalysisMonte2000}, as well as the R packages
\href{https://cran.r-project.org/web/packages/simstudy/vignettes/simstudy.html}{\texttt{simstudy}},
\citep{simstudy} and
\href{https://personality-project.org/r/psych/help/sim.html}{\texttt{psych}},
\citep{psych}.

@@

\begin{quote}
\hl{Navigate to}
 \url{https://zenodo.org/account/settings/github/}
\end{quote}

@@

Supplementary Materials{All materials (i.e., the source code, all figures, and the data) that are neccesary for reproducing the submitted version of this article are availible at \url{https://github.com/aaronpeikert/repro-tutorial} and archived under \url{https://doi.org/10.5281/zenodo.5724454}}.
